
\documentclass[10pt, leqno]{article}
\newenvironment{proof}{\noindent {\bf Proof:}}{$\Box$ \vspace{2 ex}}
\usepackage{amsmath, amssymb, amscd, hyperref, framed}
\usepackage{latexsym, epsfig, color, url, relsize, soul, cancel, textcomp}
\usepackage{pgfplots}
\usepackage{tikz, verbatim, xcolor, skull, sgame, enumitem}\renewcommand\gamestretch{2}
\usetikzlibrary{calc,matrix}
\usepackage{ifthen,environ,etoolbox, multicol}

\pgfplotsset{compat=1.18} 

\title{Polished Proof \#1}
\author{Name - Discrete Math}
\date{Due: Friday, September 16, 11pm on Gradescope.}

\begin{document}
	
\maketitle
	
\section*{Directions}
	
Complete the assignment in \LaTeX ~ on Overleaf, download the pdf and upload on Gradescope. When you complete the proof, write a reflection based on the prompt below. This should be in complete sentences and follow standard English grammatical rules.

	
\section*{Proof Options}
	
Please choose \textbf{one} of these following exercises from the textbook. Begin with ``Claim:" and write the statement you intend to prove. Then write ``Proof:" and the proof. You can choose your own end-of-proof marker for flair. 	
$$ 	5.6, 5.8, 5.12, 5.18 $$ 
	
	
\section*{Grading Rubric}
This assignment will be graded on a scale of 1-10 via the RVF rubric (9 points) discussed in class. More information on this rubric can be found \href{https://drive.google.com/file/d/1P0OBjw-GkX64uCpYcqYmXARapf9MwaiI/view?usp=sharing}{here}. \href{https://drive.google.com/file/d/1KAFQ7GBFpfUkyTBRZ30h5o6nXWwYDSML/view?usp=sharing}{Here} are some examples of past Polished Proof graded work to make sure expectations are clear. The remaining point will be given for the proper use of \LaTeX.
	
\end{document}
